Molecular alignment on graphene surface determines transport properties of graphene/organic semiconductor transistors

### 2020-04-14 manuscript.tex
many typos, but also maybe a problem with LUMO

  Graphene field-effect transistor structures were used to investigate the role of molecular alignment on charge transport properties of heterostructures comprising a single-layer graphene and variable thickness of N,N'-bis(n-octyl)-(1,7\&1,6)-dicyanoperylene-3,4:9,10-bisdicarboximide (PDI8-CN2) - an n-type organic semiconductor.
 Our atomic force microscopy data show that under selected growth conditions PDI8-CN2 grows in a layer-by-layer fashion up to a second monolayer.
 The first layer comprises flat-lying molecules, whereas the molecules in the second layer orient themselves in an upright orientation.
 Transconductance measurements show that the flat-lying molecules have little effect on the position of the Fermi level in graphene.
 Upright oriented molecules in the second layer instead, have a strong effect as to neutralize native $p$-type doping of graphene and cause a shift of charge-neutrality level towards the Dirac point.
 We interpret such behavior in terms of different orientation of the surface dipole on layers with different molecular orientations.
 At the same time the overall mobility of the charge carriers reaches values exceeding 3000 cm$^{2}$/Vs.

@@

The initial stages of growth of OSs are of particular importance also for  the graphene-based electronic devices that include OS, since in this stage the orientation of molecules on the substrate is determined.
 The geometrical orientation of the electric dipoles and multipoles depends, in turn on the orientation of the molecule on the substrate\cite{geng-2012}.
 The electric field dipole exhibits a $\propto 1/r^{3}$ dependence on the distance from the dipole and is thus important only for the extremely thin overlayes on graphene.
 In addition it is important that the overlayers are structurally coherent i.e.monocrystalline domains are as large as possible in order to reduce disorder-related reduction in the effects of surface dipoles.
 Indeed, as  we show in this work, charge carrier transport in such material systems is crucially dependent on the molecular orientation at the graphene/OS interface.
 For this type of research it is important to select an OS that exhibits high charge carrier mobility per se, in order to preserve high mobility on graphene.
   N,N'-bis(n-octyl)-(1,7\&1,6)-dicyanoperylene-3,4:9,10-bisdicarboximide (PDI8-CN2)
 exhibits a remarkable air stability, solution processability and relatively high electron mobility in thin film form\cite{jung-2014,molinari-2009,piliego-2009a}.  The position of the lowest unoccupied molecular orbital (LUMO) in this material is at 7.1 eV\cite{jung-2014}, which makes it suitable for interfacing with graphene, whose Dirac point is at $~4.5$ eV.

@@

The understanding of morphological properties of the OS layer and its growth mode is important for the interpretation of the charge transport data presented in the following.
  In organic semiconductors charge transport proceeds by hopping in a manifold of localized molecular electronic states and is thus strongly dependent on the relative orientation of the molecules and the degree of positional disorder in the layers.
  On graphene instead, charge transport is characterized by Bloch-like extended states, which reside, in the case of a single-layer graphene in a relatively disorder-free environment.
  The effect of PDI8-CN2 layers on charge transport through graphene was studied by measuring the transfer characteristics of GFETs with different amounts of PDI8-CN2 grown on graphene channel.
 Typical evolution of transconductance current for clean graphene and two different coverages is illustrated in Figure \ref{fig:3}, where we show the results of measurements (symbols) obtained on GFETs comprising clean single-layer (brown curve), GFET with PDI8-CN2 coverage of 1 minute and PDI8-CN2 (blue curve) and with coverage of 3 minutes (green curve).
 Only a forward gate sweep (from $V_g<0$ to $V_g>0$) data are shown.
 A minimal hysteresis was observed  indicating the  a relatively low density of traps that would originate from the structural and/or chemical defects in the layers.

\begin{figure}[htb]
  \centering
   \includegraphics[width=0.9\textwidth]{./Figures/fig3}  
  \caption{Transconductance measurements of a graphene field-effect transistor at different PDI8-CN2 coverages of graphene.
 Brown curve corresponds to clean graphene, blue curve corresponds to a coverage of 0.7 obtained by the PDI8-CN2 deposition of 1 minute.
 The green curve corresponds to the coverage obtained by PDI8-CN2 deposition of 4 minutes.
 The corresponding morphologies are shown in Figures 1 and 2, respectively. 
 }
  \label{fig:3}
\end{figure}

@@

At the PDI8-CN2 coverage of 0.7 the position of CNP is shifted slightly (for $\sim$0.5 V)  to more positive voltages and the current at the CNP is slightly increased relative to the clean graphene.
  More importantly, we note a less pronounced change in the slope of the transfer characteristics at negative gate voltages, compared to the one observed on clean graphene (brown curve).
 The observed behavior of the transport properties can be understood in the context of rather complex morphology of PDI8-CN2 layers on graphene, and with is associated interaction of the PDI8-CN2 molecules with graphene.
 At the sub-monolayer coverage of PDI8-CN2 the hole transport continues to proceed through the channel, relatively unhindered, electron transport, however is enhanced relative to clean graphene (cf.brown and blue curve in Figure \ref{fig:3}).

 We have noted that the crossover in the transfer curve is related to the partial depinning of the Fermi level near the contacts.
 Due to the low density of states in graphene this interface environment may extend as far as 0.
2 $\mu$m\cite{mueller-2009}.
 This is the area exposed to the flux of incoming PDI8-CN2 molecules during the organic layer growth and represents a place of nucleation of the PDI8-CN2 islands.
 The AFM results (Figure 1) show that at this coverage islands are formed in which the molecules are oriented face-on on the graphene surface.
 It has been shown\cite{su-2009} that molecules with large aromatic structures carrying surplus of negative charge are noncovalently bonded to graphene surface by $\pi-\pi$ interactions, which result in strong charge transfer at the interface.
 The additional charges that are brought to the interface by the organic molecules change the carrier concertation in graphene and change the position of the Fermi level, in the direction as to reduce the $p^{++}$ doping at the interface and therefore increase hole mobility in that region.
 The low position of LUMO in PDI8-CN2 (-4.3 eV)\cite{jones-2007} enables efficient electron transfer to graphene, reducing strong p-type doping levels near the Au contacts.
 Consequently, the cusp in the transfer curve is reduced.
   As for the small shift of CNP relative to the clean graphene, it corresponds to to the change of position of Fermi level of only ~$3\times10^{-3}$ eV, indicating negligible charge transfer between PDI8-CN2 layer and graphene, which would affect its electronic properties.
 Interestingly, the 0.7 monolayer coverage agrees nicely with the 0.5 ML--0.7ML coverage of PDI8-CN2 at which the onset of  drain-source current is observed in PDI8-CN2-based organic thin film transistors\cite{liscio-2013}.

@@

The resistance ($R=V_{G}/I_{DS}$) plots calculated from the data used to plot Figure \ref{fig:3} are shown in Figure \ref{fig:4} where we also show the results of a least-square fitting of the data (symbols) to a model function explained in the following.
In the outset we note that the drain current was calculated as:
  \begin{equation}
    \label{eq:2}
    I_{D}=\frac{W}{L}\mu n e(V_{D}- I_{D}R_{C})
  \end{equation}
  \noindent With $W$ and $L$ channel width and length respectively, $R_{C}$ the resistance of both metallic contacts, $\mu$ charge carrier mobility and $n$ their concentration.
   Given by:
  \begin{equation}
    \label{eq:3}
    n=\sqrt{n_{o}^{2}+n^{2}(V_{g})}
  \end{equation}
 Here $n_o$ represents a carrier concentration induced by charged impurities residing within the SiO$_{2}$ and arise from the reactions on its surface\cite{adam-2007}.
 $n(V_{g})$ represents surface density of charge in graphene ($n$), which depends on the gate voltage and the graphene/bottom gate capacitance.
The latter can be considered as sum of  the quantum capacitance -- dependent on the position of the  Fermi level ($E_F$)  in  graphene, 
 and the electrostatic  capacitance between the graphene layer and the gate electrode, given by $C_{ox}=(\epsilon_0\epsilon)/d_{ox}$\cite{sze-2006}.
 For the thickness of the SiO$_{2}$ $d_{ox}=$285 nm and its dielectric constant  $\epsilon \approx 3.9$,  $C_{ox}=1.2\times10^{-12}$ F cm$^{-2}$.
 The quantum capacitance has been shown to be on the order of $ \geq 8 \times10^{-7}$ F cm$^{-2}$ \cite{xia_2009}, and can therefore be ignored in our case\cite{das-2008}. 
 Therefore, the $V_{g}$-modulated carrier concentration in graphene is given by
 \begin{equation}
   \label{eq:4}
   n(V_{g})= \frac{C_{ox}}{e}(V_{g}- V_{CNP})
 \end{equation}
 \noindent With $V_{CNP}$ the gate voltage of CNP\cite{xia-2010}.
 The total resistance $R$ of the structure is the resistance of the  channel plus the resistance of the contacts and can be  obtained from (\ref{eq:2}-\ref{eq:4}):	
 \begin{equation}
	 \label{eq:5}
     R_{tot} = \frac{V_{D}}{I_{D}} = \frac{L}{W\mu e\sqrt{n_{0}^{2}+n^{2}(V_{g})}} +R_{C}
 \end{equation}
 \noindent The results of the least-square fitting of (\ref{eq:5}) to measurements are shown by black solid lines in Figure \ref{fig:4}. The fitting parameters were $R_{C}$, $\mu$, $n_0$ and $n(V_{CNP})$.
 Their  values for the three cases considered are summarised in Table \ref{tab:1}.

@@

\noindent \begin{table}[h]
  \centering
  \begin{tabular}{|l|r|r|r|r|r|r|} \hline%
   & $n_{0}$ (cm$^{-2}$ )& $R_{c}^{h}(\Omega$) & $R_{c}^{e}(\Omega)$ & $\mu_{h}$ (cm$^{2}$/Vs) & $\mu_{e}$ (cm$^{2}$/Vs) & $V_{D}(V) $  \\ \hline%
    Clean gr.
 & 3.
33$\times 10^{11}$ & 3303 $\pm$ 4 & 2469 $\pm$ 4 & 27000 $\pm$ 4000 & 16000 $\pm$ 3000 & 8.0 \\
    70\% cov.
 &3.
71$\times 10^{11}$ & 2695 $\pm$ 6 & 2262 $\pm$6 & 19000 $\pm$ 3000 & 14000 $\pm $2000 & 8.5 \\
     100\% cov.
 &7.
42$\times 10^{11}$ & 2630 $\pm$ 10 & 2550 $\pm$10 & 3500 $\pm$ 600 & 3400 $\pm$ 600 & 1.0 \\ \hline

  \end{tabular}
  \caption{The results of fitting of resistance crves shown in Figure \ref{fig:3}.
 See  text for the explantaion of the parameters.
}
  \label{tab:1}
\end{table}

@@

 The mobility of the second transport channel through OS layer is expected to be lower compared
 to mobility in graphene, due to reduced transfer intergral between molecules due to weak VdW interaction.
 Therefore, we believe that the measured mobility dependence results mainly from the mobility dependence of graphene on the
 charge density, as was theoretically predicted in Ref. \onlinecite{majorana-2016}.
 Their theoretical modeling demonstrate how the electron mobility in graphene drops with charge density.
 In our cast, the charge density is being transfered from OS adlayers.
 However such charge transfer not only increases charge density in graphene, but also pin the Fermi energy and CNP.
 The interplay between these two phenomena is expected to show complex behaviour.
 Nevertheless, our results clearly demonstrate that the first flat-lying OS layer is enough to reduce CNP.
 However, the perpenicular stacking of perylene-like molecules further increases $n_0$ and reduces carrier mobility.

@@

In conclusion, our charge transport experiments of the graphene/PDI8-CN2 heterostructures coupled with numerical modeling of the resistivity data demonstrate a crucial role that molecular orientation on graphene has on charge carrier transport properties of graphene field effect transistors with organic semiconductor channels.
  We have shown that under precisely controlled growth conditions PDI8-CN2 form a first continuous monolayer characterized by exclusively flat-lying molecules.
  Due to the orientation of the surface multipolar electric field associated with such orientation of the molecules their effect on the doping levels  of  the underlying graphene is only minor, if anything it slightly increases p-type doping of graphene.
 The growth mode of PDI8-CN2 is peculiar in the sense that it proceeds in a layer-by-layer fashion also in the second layer.
 However, the molecules in the second layer are oriented in a upright fashion, exposing the dipole electric field that stems mostly from electron withdrawing groups in such a way as to increase n-type doping of graphene, as manifested by the shift of the Fermi  level almost to the Dirac point.
  Coupled to this is also opening of another transport channel via the PDI8-CN2 topmost layer, which maintains extremely high mobility of the OS-graphene system.

>>>>

  Graphene field-effect transistor structures were used to investigate the role of molecular alignment on charge transport properties of heterostructure comprising a single-layer graphene and variable thickness of N,N'-bis(n-octyl)-(1,7\&1,6)-dicyanoperylene-3,4:9,10-bisdicarboximide (PDI8-CN2) - an n-type organic semiconductor.
 Our atomic force microscopy data show that under selected growth conditions PDI8-CN2 grows in a layer-by-layer fashion up to a second monolayer.
 The first layer comprises flat-lying molecules, whereas the molecules in the second layer orient themselves in an upright orientation.
 Transconductance measurements show that the flat-lying molecules have little effect on the position of the Fermi level in graphene.
 Upright oriented molecules in the second layer instead, have a strong effect as to neutralize native $p$-type doping of graphene and cause a shift of charge-neutrality level towards the Dirac point.
 We interpret such behavior in terms of different orientation of the surface dipole on layers with different molecular orientations.
 At the same time the overall mobility of the charge carriers reaches values exceeding 3000 cm$^{2}$/Vs.

@@

The initial stages of growth of OSs are of particular importance also for  the graphene-based electronic devices that include OS, since in this stage the orientation of molecules on the substrate is determined.
 The geometrical orientation of the electric dipoles and multipoles depends, in turn on the orientation of the molecule on the substrate\cite{geng-2012}.
 The electric field dipole exhibits a $\propto 1/r^{3}$ dependence on the distance from the dipole and is thus important only for the extremely thin overlayers on graphene.
 In addition it is important that the overlayers are structurally coherent i.e. monocrystalline domains are as large as possible in order to reduce disorder-related reduction in the effects of surface dipoles.
 Indeed, as  we show in this work, charge carrier transport in such material systems is crucially dependent on the molecular orientation at the graphene/OS interface.
 For this type of research it is important to select an OS that exhibits high charge carrier mobility per se, in order to preserve high mobility on graphene.
   N,N'-bis(n-octyl)-(1,7\&1,6)-dicyanoperylene-3,4:9,10-bisdicarboximide (PDI8-CN2)
 exhibits a remarkable air stability, solution processability and relatively high electron mobility in thin film form\cite{jung-2014,molinari-2009,piliego-2009a}.  The position of the lowest unoccupied molecular orbital (LUMO) in this material is at 7.1 eV\cite{jung-2014}, which makes it suitable for interfacing with graphene, whose Dirac point is at $~4.5$ eV.

@@

The understanding of morphological properties of the OS layer and its growth mode is important for the interpretation of the charge transport data presented in the following.
  In organic semiconductors charge transport proceeds by hopping in a manifold of localized molecular electronic states and is thus strongly dependent on the relative orientation of the molecules and the degree of positional disorder in the layers.
  On graphene instead, charge transport is characterized by Bloch-like extended states, which reside, in the case of a single-layer graphene in a relatively disorder-free environment.
  The effect of PDI8-CN2 layers on charge transport through graphene was studied by measuring the transfer characteristics of GFETs with different amounts of PDI8-CN2 grown on graphene channel.
 Typical evolution of transconductance current for clean graphene and two different coverages is illustrated in Figure \ref{fig:3}, where we show the results of measurements obtained on GFETs comprising clean single-layer (orange curve), GFET with PDI8-CN2 coverage of 1 minute (blue curve) and PDI8-CN2 coverage of 3 minutes (green curve).
 Only a forward gate sweep (from $V_g<0$ to $V_g>0$) data are shown.
 A minimal hysteresis was observed  indicating relatively low density of traps that would originate from the structural and/or chemical defects in the layers.

\begin{figure}[htb]
  \centering
   \includegraphics[width=0.9\textwidth]{./Figures/fig3}  
  \caption{Transconductance measurements of a graphene field-effect transistor at different PDI8-CN2 coverages of graphene.
 Orange curve corresponds to clean graphene, blue curve corresponds to a coverage of 0.7 obtained by the PDI8-CN2 deposition of 1 minute.
 The green curve corresponds to the coverage obtained by PDI8-CN2 deposition of 4 minutes.
 The corresponding morphologies are shown in Figures 1 and 2, respectively. 
 }
  \label{fig:3}
\end{figure}

@@

At the PDI8-CN2 coverage of 0.7 the position of CNP is shifted slightly (for $\sim$0.5 V)  to more positive voltages and the current at the CNP is slightly increased relative to the clean graphene.
  More importantly, we note a less pronounced change in the slope of the transfer characteristics at negative gate voltages, compared to the one observed on clean graphene (orange curve).
 The observed behavior of the transport properties can be understood in the context of rather complex morphology of PDI8-CN2 layers on graphene, and with its associated interaction of the PDI8-CN2 molecules with graphene.
 At the sub-monolayer coverage of PDI8-CN2 the hole transport continues to proceed through the channel, relatively unhindered, electron transport, however is enhanced relative to clean graphene (cf.orange and blue curve in Figure \ref{fig:3}).

 We have noted that the crossover in the transfer curve is related to the partial depinning of the Fermi level near the contacts.
 Due to the low density of states in graphene this interface environment may extend as far as 0.2 $\mu$m\cite{mueller-2009}.
 This is the area exposed to the flux of incoming PDI8-CN2 molecules during the organic layer growth and represents a place of nucleation of the PDI8-CN2 islands.
 The AFM results (Figure 1) show that at this coverage islands are formed in which the molecules are oriented face-on on the graphene surface.
 It has been shown\cite{su-2009} that molecules with large aromatic structures carrying surplus of negative charge are noncovalently bonded to graphene surface by $\pi-\pi$ interactions, which result in strong charge transfer at the interface.
 The additional charges that are brought to the interface by the organic molecules change the carrier concentrations in graphene and change the position of the Fermi level, in the direction as to reduce the $p^{++}$ doping at the interface and therefore increase hole mobility in that region.
 The low position of LUMO in PDI8-CN2 (-4.3 eV)\TODO{Which is correct? One in introduction is 7.1, this one is 4.3}\cite{jones-2007} enables efficient electron transfer to graphene, reducing strong p-type doping levels near the Au contacts.
 Consequently, the cusp in the transfer curve is reduced.
   As for the small shift of CNP relative to the clean graphene, it corresponds to to the change of position of Fermi level of only ~$3\times10^{-3}$ eV, indicating negligible charge transfer between PDI8-CN2 layer and graphene, which would affect its electronic properties.
 Interestingly, the 0.7 monolayer coverage agrees nicely with the 0.5 ML--0.7ML coverage of PDI8-CN2 at which the onset of  drain-source current is observed in PDI8-CN2-based organic thin film transistors\cite{liscio-2013}.

@@

The resistance ($R=V_{G}/I_{DS}$) plots calculated from the data used to plot Figure \ref{fig:3} are shown in Figure \ref{fig:4} where we also show the results of a least-square fitting of the data (symbols) to a model function explained in the following.
In the outset we note that the drain current was calculated as:
  \begin{equation}
    \label{eq:2}
    I_{D}=\frac{W}{L}\mu n e(V_{D}- I_{D}R_{C})
  \end{equation}
  \noindent With $W$ and $L$ channel width and length respectively, $R_{C}$ the resistance of both metallic contacts, $\mu$ charge carrier mobility and $n$ their concentration.
   Given by:
  \begin{equation}
    \label{eq:3}
    n=\sqrt{n_{o}^{2}+n^{2}(V_{g})}
  \end{equation}
 Here $n_o$ represents a carrier concentration induced by charged impurities residing within the SiO$_{2}$ and arise from the reactions on its surface\cite{adam-2007}.
 $n(V_{g})$ represents surface density of charge in graphene ($n$), which depends on the gate voltage and the graphene/bottom gate capacitance.
The latter can be considered as sum of serially connected quantum capacitance -- dependent on the position of the  Fermi level ($E_F$)  in  graphene, 
 and the electrostatic  capacitance between the graphene layer and the gate electrode, given by $C_{ox}=(\epsilon_0\epsilon)/d_{ox}$\cite{sze-2006}.
 For the thickness of the SiO$_{2}$ $d_{ox}=$285 nm and its dielectric constant  $\epsilon \approx 3.9$,  $C_{ox}=1.2\times10^{-12}$ F cm$^{-2}$.
 The quantum capacitance has been shown to be on the order of $ \geq 8 \times10^{-7}$ F cm$^{-2}$ \cite{xia_2009}, and can therefore be ignored in our case\cite{das-2008}. 
 Therefore, the $V_{g}$-modulated carrier concentration in graphene is given by
 \begin{equation}
   \label{eq:4}
   n(V_{g})= \frac{C_{ox}}{e}(V_{g}- V_{CNP})
 \end{equation}
 \noindent With $V_{CNP}$ the gate voltage of CNP\cite{xia-2010}.
 The total resistance $R$ of the structure is the resistance of the  channel plus the resistance of the contacts and can be  obtained from (\ref{eq:2}-\ref{eq:4}):	
 \begin{equation}
	 \label{eq:5}
     R_{tot} = \frac{V_{D}}{I_{D}} = \frac{L}{W\mu e\sqrt{n_{0}^{2}+n^{2}(V_{g})}} +R_{C}
 \end{equation}
 \noindent The results of the least-square fitting of (\ref{eq:5}) to measurements are shown by black solid lines in Figure \ref{fig:4}. The fitting parameters were $R_{C}$, $\mu$, $n_0$ and $V_{CNP}$.
 Their  values for the three cases considered are summarized in Table \ref{tab:1}.

@@

\noindent \begin{table}[h]
  \centering
  \begin{tabular}{|l|r|r|r|r|r|r|} \hline%
   & $n_{0}$ (cm$^{-2}$ )& $R_{c}^{h}(\Omega$) & $R_{c}^{e}(\Omega)$ & $\mu_{h}$ (cm$^{2}$/Vs) & $\mu_{e}$ (cm$^{2}$/Vs) & $V_{D}(V) $  \\ \hline%
    Clean gr.
 & 3.33$\times 10^{11}$ & 3303 $\pm$ 4 & 2469 $\pm$ 4 & 27000 $\pm$ 4000 & 16000 $\pm$ 3000 & 8.0 \\ 
 70\% cov. %dont break line after decimal point
 &3.71$\times 10^{11}$ & 2695 $\pm$ 6 & 2262 $\pm$6 & 19000 $\pm$ 3000 & 14000 $\pm $2000 & 8.5 \\ 
 100\% cov.
 &7.42$\times 10^{11}$ & 2630 $\pm$ 10 & 2550 $\pm$10 & 3500 $\pm$ 600 & 3400 $\pm$ 600 & 1.0 \\ \hline
  \end{tabular}
  \caption{The results of fitting of resistance curves shown in Figure \ref{fig:3}.
 See  text for the explanation of the parameters.
}
  \label{tab:1}
\end{table}

@@

 The mobility of the second transport channel through OS layer is expected to be lower compared
 to mobility in graphene, due to reduced transfer integral between molecules due to weak VdW interaction.
 Therefore, we believe that the measured mobility dependence results mainly from the mobility dependence of graphene on the
 charge density, as was theoretically predicted in Ref. \onlinecite{majorana-2016}.
 Their theoretical modeling demonstrate how the electron mobility in graphene drops with charge density.
 In our cast, the charge density is being transferred from OS adlayers.
 However such charge transfer not only increases charge density in graphene, but also pin the Fermi energy and CNP.
 The interplay between these two phenomena is expected to show complex behavior.
 Nevertheless, our results clearly demonstrate that the first flat-lying OS layer is enough to reduce CNP.
 However, the perpendicular stacking of perylene-like molecules further increases $n_0$ and reduces carrier mobility.

@@

In conclusion, our charge transport experiments of the graphene/PDI8-CN2 heterostructure coupled with numerical modeling of the resistivity data demonstrate a crucial role that molecular orientation on graphene has on charge carrier transport properties of graphene field effect transistors with organic semiconductor channels.
  We have shown that under precisely controlled growth conditions PDI8-CN2 form a first continuous monolayer characterized by exclusively flat-lying molecules.
  Due to the orientation of the surface multipolar electric field associated with such orientation of the molecules their effect on the doping levels  of  the underlying graphene is only minor, if anything it slightly increases p-type doping of graphene.
 The growth mode of PDI8-CN2 is peculiar in the sense that it proceeds in a layer-by-layer fashion also in the second layer.
 However, the molecules in the second layer are oriented in a upright fashion, exposing the dipole electric field that stems mostly from electron withdrawing groups in such a way as to increase n-type doping of graphene, as manifested by the shift of the Fermi  level almost to the Dirac point.
  Coupled to this is also opening of another transport channel via the PDI8-CN2 topmost layer, which maintains extremely high mobility of the OS-graphene system.
